Keras + MNIST
===============

Keras is a high-level neural networks API developed with a focus on enabling fast experimentation. 
Keras has the following key features:
  - Allows the same code to run on CPU or on GPU, seamlessly.
  - User-friendly API which makes it easy to quickly prototype deep learning models.
  - Built-in support for convolutional networks (for computer vision), recurrent networks (for sequence processing), and any combination of both..
  - Supports arbitrary network architectures: multi-input or multi-output models, layer sharing, model sharing, etc. This means that Keras is appropriate for building essentially any deep learning model, from a memory network to a neural Turing machine.
  - Is capable of running on top of multiple back-ends including TensorFlow, CNTK, or Theano.

```{r}

```

Preparing the Data
=====================
The MNIST dataset is included with Keras and can be accessed using the dataset_mnist() function. Here we load the dataset then create variables for our test and training data:
```{r}

```


```{r}
#install.packages("keras")
#library(keras)
#install_keras()
```

```{r}
library(keras)
mnist <- dataset_mnist()
x_train <- mnist$train$x
y_train <- mnist$train$y
x_test <- mnist$test$x
y_test <- mnist$test$y

# x data is 3D
x_train[1,1,1]


```

The x data is a 3-d array (images,width,height) of grayscale values . To prepare the data for training we convert the 3-d arrays into matrices by reshaping width and height into a single dimension (28x28 images are flattened into length 784 vectors). Then, we convert the grayscale values from integers ranging between 0 to 255 into floating point values ranging between 0 and 1:

Note that we use the array_reshape() function rather than the dim<-() function to reshape the array. This is so that the data is re-interpreted using row-major semantics (as opposed to R’s default column-major semantics), which is in turn compatible with the way that the numerical libraries called by Keras interpret array dimensions.

```{r}
# reshape
x_train <- array_reshape(x_train, c(nrow(x_train), 784))
x_test <- array_reshape(x_test, c(nrow(x_test), 784))
# rescale
x_train <- x_train / 255
x_test <- x_test / 255

# x data reshaped to 2D
x_train[1,1]


```

The y data is an integer vector with values ranging from 0 to 9. To prepare this data for training we one-hot encode the vectors into binary class matrices using the Keras to_categorical() function:

```{r}
y_train <- to_categorical(y_train, 10)
y_test <- to_categorical(y_test, 10)

y_train[1]

```

Defining the Model
The core data structure of Keras is a model, a way to organize layers. The simplest type of model is the Sequential model, a linear stack of layers.

We begin by creating a sequential model and then adding layers using the pipe (%>%) operator:

```{r}
model <- keras_model_sequential() 
model %>% 
  layer_dense(units = 256, activation = 'relu', input_shape = c(784)) %>% 
  layer_dropout(rate = 0.4) %>% 
  layer_dense(units = 128, activation = 'relu') %>%
  layer_dropout(rate = 0.3) %>%
  layer_dense(units = 10, activation = 'softmax')
```


The input_shape argument to the first layer specifies the shape of the input data (a length 784 numeric vector representing a grayscale image). The final layer outputs a length 10 numeric vector (probabilities for each digit) using a softmax activation function.

Use the summary() function to print the details of the model:

```{r}
summary(model)
```

Next, compile the model with appropriate loss function, optimizer, and metrics:

```{r}
model %>% compile(
  loss = 'categorical_crossentropy',
  optimizer = optimizer_rmsprop(),
  metrics = c('accuracy')
)

```


Training and Evaluation
Use the fit() function to train the model for 30 epochs using batches of 128 images:

```{r}
history <- model %>% fit(
  x_train, y_train, 
  epochs = 30, batch_size = 128, 
  validation_split = 0.2
)
```

The history object returned by fit() includes loss and accuracy metrics which we can plot:

```{r}
plot(history)
```

Evaluate the model’s performance on the test data:

```{r}
model %>% evaluate(x_test, y_test)
```

Generate predictions on new data:

```{r}
model %>% predict_classes(x_test)
```


